Discrete Quantum Theories and Computing

### 2018-02-15 prop_letter_ajhs_referee_response.tex

The first lemma shows a simpler way to prove the convexity
condition. Recall that convexity condition for a QIVPM
$\mu : \events \rightarrow \mathscr{I}$ states that for each pair of
\emph{commuting} projectors~$P$ and~$P'$ with $PP'=P'P$, the following
equation holds:
\begin{equation}
\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(P'\right)\,.
\end{equation}

\begin{lemma}
  To verify the convexity condition of a QIVPM
  $\mu : \events \rightarrow \mathscr{I}$, it is sufficient to verify
  that for all orthogonal projectors $P_{0}$ and~$P_{1}$, we have
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.\label{amr}
\end{equation}
\end{lemma}
\noindent The proof follows the outline of the proof of the classical
inclusion-exclusion principle. From the commuting projectors $P$ and
$P'$, we construct the following three orthogonal projectors $PP'$,
$P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
follows: {\footnotesize
\[\begin{array}{rcl}
&& \bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
&& \hfill(\mbox{because } P = PP' + P - PP') \\
&=& \bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) \\
&=& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
&& \hfill(\mbox{because } P' = PP' + P' - PP') \\
&=& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) \\
&& \hfill(\mbox{using Eq.~(2) twice}) \\
&=&
    \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
    \bar{\mu}\left(PP'\right) \\
&& \hfill(\mbox{using Eq.~(2) twice}) \\
&=&
    \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') \\
&=&
    \bar{\mu}(P) + \bar{\mu}(P')
\end{array}\]}

The next lemma relates $\delta$-deterministic QIVPMs with $\delta <
\frac{1}{3}$ to 0-deterministic QIVPMs.

\begin{lemma} 
  From any $\delta$-deterministic
  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ with
  $\delta < \frac{1}{3}$, we can construct a $0$-deterministic QIVPM
  $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
    \imposs,\necess\right\}$ defined as follows:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}
\end{lemma}
\noindent The most important part of the proof is to verify the convexity
condition for $\bar{\mu}^{\textrm{D}}$. By Lemma~2.1, it is sufficient
to verify the following equation for orthogonal projectors $P_{0}$
and~$P_{1}$,
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,. \label{eq:QuantumInterval-valuedProbability-Equal}
\end{equation}

@@

When one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
is $\necess$, say $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\imposs$
and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\necess$, we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
and $\bar{\mu}\left(P_{1}\right)\subseteq\left[1-\delta,1\right]$ which
implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[1-\delta,1+\delta\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of $\left[0,1\right]$,
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[1-\delta,1\right]$,
which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)$ is also
$\necess$ satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).

When both
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$ and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$
are $\imposs$, we have both $\bar{\mu}\left(P_{0}\right)$ and
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
Since we assume $\delta<\frac{1}{3}$, $\left[0,2\delta\right]$ and
$\left[1-\delta,1\right]$ are disjoint, which implies
$\bar{\mu}\left(P_{0}+P_{1}\right)$ and $\left[1-\delta,1\right]$ are
disjoint. Together with the fact that
$\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either
$\left[0,\delta\right]$ or $\left[1-\delta,1\right]$,
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
$\left[0,\delta\right]$, which implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$ and hence
also satisfying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).
